Experimental and numerical studies of the effects of resonant and random excitations of the proton beam in the LHC, with applications to the design of a pulsed hollow electron lens for active halo control

### 2018-03-05 resex.tex
Revised figure of beam profiles in 10th-turn experiments. Added general reference to Trad's thesis for BSRT. Updated to-do list.

During the experiments, losses were measured with the fast beam
current transformers (FBCTs). Transverse beam profiles and emittances
were provided by the beam synchrotron radiation telescope (BSRT). All
instruments were capable of delivering bunch-by-bunch data. The data
analysis of the BSRT profiles is quite involved. In this paper, we
focus on the direct comparison of the resulting profiles. A detailed
description of the profile analysis can be found in
Ref.~\cite{bsrtprofinj}, with individual experiments reported in
Refs.~\cite{resexmd2016, resexmd2017}.

@@

\begin{figure*}
  \begin{tabular}{ccc}
    \includegraphics[width=0.32\textwidth]{2016_bunch_intensity_v10th_no_damper_avg.png}&
    \includegraphics[width=0.32\textwidth]{2016_emith_avg_rel_v10th_no_damper.png}&
    \includegraphics[width=0.32\textwidth]{2016_emitv_avg_rel_v10th_no_damper.png}\\
  \end{tabular}
  \caption{Summary of the 2016 experiments on $10^{\mathrm{th}}$~turn
    pulsing in the vertical plane: losses (left), horizontal
    emittances (middle) and vertical emittances (right), relative to
    their initial values. The transverse damping system was not active
    in this case. The 3 excitation periods are labeled in black
    according to the value of the maximum excitation amplitude
    $A_{\mathrm{max}} = 5 \, \Delta A$: no excitation, 48~nrad or
    96~nrad. The 4~bunches experiencing the same excitation amplitude
    $n \, \Delta A$ ($n = 0, \ldots, 5$) are grouped by color. The
    data are averaged over the 4~bunches, with the envelope
    representing the standard deviation. The area with a blue
    background highlights qualitatively the fast adjustment period of
    the beam distribution transitioning into a new equilibrium state
    (indicated by the gray background).}
  \label{fig:10thexp}
\end{figure*}

\begin{figure*}
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		reference bunch, no excitation
		\includegraphics[width=1.0\linewidth]{profile_v_10thv_slot_50.png}
	\end{minipage}
	\begin{minipage}[t]{0.49\linewidth}
		\centering
		excited bunch, $10^{\mathrm{th}}$~turn V		\includegraphics[width=1.0\linewidth]{profile_v_10thv_slot_1300.png}
	\end{minipage}
	\caption{\label{fig:10thexpprof} Vertical beam profiles measured with the Beam Synchrotron Radiation Telescope (BSRT) during the 2016 experiments. The profiles are taken at the end of the $10^{\mathrm{th}}$~turn pulsing in V. For both bunches the transverse damper is not active. The black line in the plot of the residual is the current profile minus the profile before applying the excitation and is a measure for the overall change of the distribution. The red line is the current profile minus its Gaussian fit, which gives and indication for the deviation of the distribution from a Gaussian distribution. For details on the analysis it is referred to \cite{bsrtprofinj}. The distribution of the reference bunch (left), here slot 50, stays unchanged, while the bunch experiencing the maximum excitation (right), here slot 1300, clearly shows a change to a non-Gaussian distribution.}
\end{figure*}

@@

Distribution changes could also be directly observed, thanks to the
performance of the Beam Synchrotron Radiation Telescope
(BSRT)~\cite{bsrtprofinj}. As an example, Fig.~\ref{fig:10thexpprof}
shows the vertical profile of a reference bunch and of a bunch
experiencing the maximum excitation
$A_{\mathrm{max}} = 5 \, \Delta A = \q{48}{nrad}$ and later
96~nrad. While the reference bunch stays unchanged, the distribution
of the excited bunch clearly changes and re-adjusts to a non-Gaussian
shape, with particles shifting from the core towards the regions at
approximately $\pm 2\sigma$. This behavior is similar to what was
calculated in simulations, as discussed in Section~\ref{sec:pattern}
and in Fig.~\ref{fig:patternhist}.

>>>>

During the experiments, losses were measured with the fast beam
current transformers (FBCTs). Transverse beam profiles and emittances
were provided by the beam synchrotron radiation telescope
(BSRT)~\cite{Trad:PhD:2015}. All instruments were capable of
delivering bunch-by-bunch data. The data analysis of the BSRT profiles
is quite involved. In this paper, we focus on the direct comparison of
the resulting profiles. A detailed description of the profile analysis
can be found in Ref.~\cite{bsrtprofinj}, with individual experiments
reported in Refs.~\cite{resexmd2016, resexmd2017}.

@@

\begin{figure*}
  \begin{tabular}{ccc}
    \includegraphics[width=0.32\textwidth]{2016_bunch_intensity_v10th_no_damper_avg.png}&
    \includegraphics[width=0.32\textwidth]{2016_emith_avg_rel_v10th_no_damper.png}&
    \includegraphics[width=0.32\textwidth]{2016_emitv_avg_rel_v10th_no_damper.png}\\
  \end{tabular}
  \caption{Summary of the 2016 experiments on $10^{\mathrm{th}}$~turn
    pulsing in the vertical plane: losses (left), horizontal
    emittances (middle) and vertical emittances (right), relative to
    their initial values. The transverse damping system was not active
    in this case. The 3 excitation periods are labeled in black
    according to the value of the maximum excitation amplitude
    $A_{\mathrm{max}} = 5 \, \Delta A$: no excitation, 48~nrad or
    96~nrad. The 4~bunches experiencing the same excitation amplitude
    $n \, \Delta A$ ($n = 0, \ldots, 5$) are grouped by color. The
    data are averaged over the 4~bunches, with the envelope
    representing the standard deviation. The area with a blue
    background highlights qualitatively the fast adjustment period of
    the beam distribution, transitioning into a new equilibrium state
    (indicated by the gray background).}
  \label{fig:10thexp}
\end{figure*}

\begin{figure*}
  \begin{tabular}{cc}
    Reference bunch, no excitation & Excited bunch, maximum amplitude \\
    \includegraphics[width=0.48\textwidth]{profile_v_10thv_slot_50.png} &
    \includegraphics[width=0.48\textwidth]{profile_v_10thv_slot_1300.png}\\
    \end{tabular}
    \caption{Vertical beam profiles measured with the Beam Synchrotron
      Radiation Telescope (BSRT) during the 2016 experiments on
      $10^{\mathrm{th}}$~turn pulsing in the vertical plane. The
      transverse damping system was not active on these bunches. The
      beam distributions at the end of the excitation period are shown
      in black in the top plots, with a Gaussian fit in red. The
      bottom plots show the residuals: final profile minus initial
      profile (black); final profile minus its Gaussian fit
      (red). Residuals are expressed as a fraction of the peak profile
      amplitude. The black lines in the plots of the residuals are a
      measure of the overall change of the distribution shape. The red
      lines indicate how different the final distributions are from a
      Gaussian shape. Details of the analysis are given in
      Ref.~\cite{bsrtprofinj}. The distribution of the reference bunch
      (left) is almost unchanged, whereas the bunch experiencing the
      maximum excitation (right) shows a clear shift of particles from
      the axis towards approximately $\pm 2\sigma$.}
    \label{fig:10thexpprof}
\end{figure*}

@@

Distribution changes could also be directly observed, thanks to the
performance of the Beam Synchrotron Radiation Telescope
(BSRT)~\cite{Trad:PhD:2015, bsrtprofinj}. As an example,
Fig.~\ref{fig:10thexpprof} shows the vertical profile of a reference
bunch and of a bunch experiencing the maximum excitation
$A_{\mathrm{max}} = 5 \, \Delta A = \q{48}{nrad}$ and later
96~nrad. While the reference bunch stays unchanged, the distribution
of the excited bunch clearly changes and re-adjusts to a non-Gaussian
shape, with particles shifting from the core towards the regions at
approximately $\pm 2\sigma$. This behavior is similar to what was
calculated in simulations, as discussed in Section~\ref{sec:pattern}
and in Fig.~\ref{fig:patternhist}.
